Relative parabolic factorizations of Chevalley groups

### 2015-08-03 paper.tex
Chevalley-Matsumoto proof finished and placed in a different place

The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
%TODO: Recheck the statement of the lemma; finish the proof.
\begin{lemma}\label{lemma:Chevalley-Matsumoto}
Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
\end{lemma} \begin{proof}  For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}). \end{proof}

@@

>>>>

@@

The following lemma is a relative version of the classical result sometimes called Chevalley---Matsumoto decomposition.
\begin{lemma}\label{lemma:Chevalley-Matsumoto}
Let $\pi$ be the fundamental representation of $\G_{sc}(\Phi, R)$ with the highest weight $\varpi_s$.
Assume that $g\in \G_{sc}(\Phi, R, I)$ is such that $(g\cdot v^+)_{\varpi\ssub{s}}=1$, then 
$g \in \U(\Sigma_s^-, I) \cdot \G_{sc}(\Delta_s, R, I) \cdot \U(\Sigma_s^+, I)$.
\end{lemma}
\begin{proof}
For $I=R$ the statement of the lemma is contained in~\cite[Theorem~1.3]{St78}). So we can write $g=u_1\cdot g'\cdot u_2$, where $u_1\in\U(\Sigma_s^-,R)$, $u_2\in\U(\Sigma_s^+,R)$ and $g'\in\G(\Delta_s,R)$. Since $g\in\G(\Phi,R,I)$, the vector $gv^+$ is $I$-unimodular. On the other hand, $g'u_2v^+=v^+$, so $u_1\in\G(\Phi,R,I)\cap\U(\Sigma_s^-,R)=\U(\Sigma_s^-,I)$. Now $g'u_2\in\left(\G(\Delta_s,R)\U(\Sigma_s^+,R)\right)\cap\G(\Phi,R,I)$, and by Levi decomposition $u_2\in\U(\Sigma_s^+,I)$, $g'\in\G(\Delta_s,R,I)$.
\end{proof}
